Evidence of the necessity of isotopic precise calculation in fuel cycle calculation

### 2016-07-01 paper.tex
remove nad lines...
correct 1 typo...

Because the neural network model allows only to mix a plutonium stream into a
uranium stream, slight modification have been made on the cycle: in both ``J1''
and ``E3'' streams uranium and plutonium are separated, the uranium and
plutonium sub-streams are mix together to build one stream of pure uranium and
one stream of pure plutonium. That is why, when comparing the different fuel
fabrication models only the total plutonium enrichement are compared.

@@

Another analysis was performed to evaluate the impact of the depletion
calculation on a fuel cycle macroscopic (???) level.

>>>>

Because the neural network model allows only to mix a plutonium stream into a
uranium stream, slight modification have been made on the cycle: in both ``J1''
and ``E3'' streams uranium and plutonium are separated, the uranium and
plutonium sub-streams are mix together to build one stream of pure uranium and
one stream of pure plutonium. That is why, when comparing the different fuel
fabrication models only the total plutonium enrichment are compared.

@@
